---
title: "BA analysis"
author: "MJ, EHS, HM"
date: "created: 10/14/2020, last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Setup
```{r}
#Set working directory
setwd("/Users/matilde/Desktop/AU/Bachelor project/Color_matching/analysis")
#Clean environment
rm(list = ls())
#Load packages
pacman::p_load(readr,dplyr,plyr,lme4,lmerTest,mgcv,tidyverse, scales)
#Load
pacman::p_load(readr,tidyverse,ggplot2,pastecs,ez,reshape2,stringr,lme4,stats,MuMIn,broom,emmeans,afex,lmerTest,scales,rstatix,ggpubr,magrittr,stats)
```

#Loading and some extra wrangling
```{r}
#Loading data
data <- read_csv("Cleaned_data/color_matching2021-01-06.csv")

#Rescale Confidence
data$Confidence <- rescale(data$Confidence, to = c(1, 7))

#Rescale Chain
data$Chain <- rescale(data$Chain, to = c(1, 6))

#Rescale Generation
data$Generation <- rescale(data$Generation, to = c(1, 15))

#Remove unfinished chain
data <- data %>% filter(!Chain=="6")

#As factors
data$Subject <- as.factor(data$Subject)
data$Language <- as.factor(data$Language)
data$Gender <- as.factor(data$Gender)
data$Language_spoken <- as.factor(data$Language_spoken)
data$Condition <- as.factor(data$Condition)
data$Chain <- as.factor(data$Chain)
data$Color_label_source <- as.factor(data$Color_label_source)
data$Color_label_matched <- as.factor(data$Color_label_matched)


#Create column classification of native language into: Danish, English, Danish bilingual and other
data$Language_class <- revalue(data$Language_spoken,c("dansk" = "Danish", "danish" = "Danish","dansker" = "Danish","Dansk" = "Danish","DK"="Danish","Engelsk" = "English", "EnglishandArabic" = "English", "DanskEngelsk" = "Bilingual", "Danskfransk" = "Bilingual", "DanskogBosnisk" = "Bilingual","Danskogengelsk" = "Bilingual", "Danskogsomalisk" = "Bilingual", "NederlandskDansk" = "Bilingual", "Dansksomalisk" = "Bilingual", "Albansk" = "Other", "Croatian" = "Other", "Czech" = "Other", "Estonian" = "Other", "Fransk" = "Other", "geman" = "Other", "German" = "Other", "GermanAfrikaans" = "Other", "Greek" = "Other", "Hollandsk" = "Other", "ita" = "Other", "Lithuanian" = "Other", "Lykke" = "Other", "Polish" = "Other", "polish" = "Other", "portuguese" = "Other", "Romanian" = "Other", "rumænsk" = "Other", "Russian" = "Other", "somalisk" = "Other", "spanish" = "Other", "Spanish" = "Other", "Svensk" = "Other", "Swedish" = "Other", "Ukrainian" = "Other", "Ungarsk" = "Other"))

#Rename gender for prettier plots
data$Gender <- ifelse(data$Gender == "female", "Female", "Male")

#Write datafile for visualisations
write.csv(data, "data.csv")
```


#Subsets
```{r}
#Datasets divided into Danish and English
danish <- data %>% filter(Language == "Danish")
english <- data %>% filter(Language == "English") %>% filter(!Chain=="2")
#Subset for each condition
cond1_danish <- danish %>% filter(Condition==1)
cond2_danish <- danish %>% filter(Condition==2)
cond1_english <- english %>% filter(Condition==1)
cond2_english <- english %>% filter(Condition==2)

#Subsets by color
d_red <- danish %>% filter(Color_label_matched == "seed dark rose")
d_yellow <- danish %>% filter(Color_label_matched == "seed mustard")
d_green <- danish %>% filter(Color_label_matched == "seed grass green")
d_blue <- danish %>% filter(Color_label_matched == "seed ocean blue")

#Subsets by color AND condition
d_red_cond1 <- d_red %>% filter(Condition=="1")
d_red_cond2 <- d_red %>% filter(Condition=="2")
d_yellow_cond1 <- d_yellow %>% filter(Condition=="1")
d_yellow_cond2 <- d_yellow %>% filter(Condition=="2")
d_green_cond1 <- d_green %>% filter(Condition=="1")
d_green_cond2 <- d_green %>% filter(Condition=="2")
d_blue_cond1 <- d_blue %>% filter(Condition=="1")
d_blue_cond2 <- d_blue %>% filter(Condition=="2")

```

#Demographics
Code used to generate demographic table (Table 1 in thesis)
```{r}
#Dataframe with 1 row pr subject 
unique <- data[ !duplicated(data$Subject,fromLast=TRUE), ]
unique_danish <- danish[ !duplicated(danish$Subject,fromLast=TRUE), ]
unique_english <- english[ !duplicated(english$Subject,fromLast=TRUE), ]

#Amount of subjects in each language
unique %>% count("Language")

#Amount of subject in each condition for each version
unique_danish %>% count("Condition") 
unique_english %>% count("Condition") 

#Gender
#Across conditions
unique_danish %>% count("Gender") 
(100/150) * 82
(100/150) * 68
unique_english %>% count("Gender")
(100/30) * 14
(100/30) * 16

#For each condition
unique_danish %>% filter(Condition=="1") %>% count("Gender") 
(100/75) * 43
(100/75) * 32
unique_danish %>% filter(Condition=="2") %>% count("Gender")
(100/75) * 39 
(100/75) * 36

unique_english %>% filter(Condition=="1") %>% count("Gender") 
(100/15) * 4
(100/15) * 11
unique_english %>% filter(Condition=="2") %>% count("Gender") 
(100/15) * 10
(100/15) * 5

#Age
#Across condition
unique_danish %>% get_summary_stats(Age,type = "mean_sd")
unique_english %>% get_summary_stats(Age,type = "mean_sd")

#For each condition
unique_danish %>% filter(Condition=="1") %>% get_summary_stats(Age,type = "mean_sd")
unique_danish %>% filter(Condition=="2") %>% get_summary_stats(Age,type = "mean_sd")
unique_english %>% filter(Condition=="1") %>% get_summary_stats(Age,type = "mean_sd")
unique_english %>% filter(Condition=="2") %>% get_summary_stats(Age,type = "mean_sd")

#Native languages
#Across conditions
unique_danish %>% count("Language_class")
(100/150) * 134
(100/150) * 1
(100/150) * 6
(100/150) * 9
unique_english %>% count("Language_class")
(100/30) * 20
(100/30) * 5

#For each condition
unique_danish %>%  filter(Condition=="1") %>% count("Language_class")
100/75 * 64
100/75 * 4
100/75 * 8
unique_danish %>%  filter(Condition=="2") %>% count("Language_class")
100/75 * 70
100/75 * 1
100/75 * 3

unique_english %>%  filter(Condition=="1") %>% count("Language_class")
100/15 * 10
100/15 * 2
100/15 * 3
unique_english %>%  filter(Condition=="2") %>% count("Language_class")

```

#Descriptive statistics
For Danish version only (included in the thesis as Tables 2 and 3) 
```{r}
detach(package:plyr)    
library(dplyr)
#RHAD: maximum, minimum, mean, and standard deviations
#Hue match: maximum, minimum,mean 
#Hue of seed and unique colors
#Error rate: mean and standard deviations
stats_hue <- danish %>% 
  group_by(Condition,Color_label_matched) %>% 
  summarise(max(RHAD),min(RHAD),mean(RHAD), sd(RHAD),max(Hue_matched),min(Hue_matched),mean(Hue_matched), mean(Seed), mean(Unique_hue), mean(Error_rate_hue), sd(Error_rate_hue), mean(Confidence)) %>% 
  arrange(Color_label_matched)

#Saturation: maximum, minimum, mean, and standard deviations
stats_sat <- data %>% 
  group_by(Color_label_matched, Condition) %>% 
  summarise(max(Saturation_matched),min(Saturation_matched),mean(Saturation_matched), sd(Saturation_matched), mean(Error_rate_sat))

```

#Testing model assumptions:
Normality checks:
Data must fall more or less on the line in the qq-plots for it to be normally distributed. From the shapiro test we see that most of the p-values are > 0.05 implying that the distribution of the data are not significantly different from normal distribution. In other words, we can assume the normality.
```{r}
##Checking HUE
#Normality (Shapiro-Wilks)
norm_hue <- danish %>% group_by(Chain, Condition, Color_label_matched) %>% shapiro_test(RHAD) %>% arrange(Color_label_matched)
#QQ-plots
ggqqplot(danish, "RHAD", ggtheme = theme_bw()) +
  facet_grid(Condition + Color_label_matched ~ Chain, labeller = "label_both")

##Checking Saturation
#Normality (Shapiro-Wilks)
norm_sat <- danish %>% group_by(Chain, Condition, Color_label_matched) %>% shapiro_test(Saturation_matched)
#QQ-plots
ggqqplot(danish, "Saturation_matched", ggtheme = theme_bw()) +
  facet_grid(Condition + Color_label_matched ~ Chain, labeller = "label_both")

```


#Modeling Saturation 
Model comparisons + model runs based on Winter & Wieler 2016 (see method section in thesis for further explanations)
```{r}
## Constructing a mixed model with random slopes for generation, condition and interaction between generation and condition by color, chain, and subjects in chain:
sat_all <- lmer(
  Saturation_matched ~ Generation + Condition + Generation:Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

```
Explanation:
 - mixed model, modeling level of saturation as a function of generation, condition (presense of color term or not), and the interaction of these with random intercepts (by-chain variation in level of saturation, by-color variation in level of saturation, and by-subject in chain variation in level of saturation) and random slopes for generation, condition and the interaction between generation and condition (by-chain/color/subject variation in the slope of generation, condition and the interaction between generation and condition) and a random intercept / slope correlation. We set REML = T because we want to perform likelihood ratio tests comparing the random effects (for fixed effects it should be REML = F)
(The estimates for the variance of the random effects are better when using REML = T.) 

Testing random effects:
```{r}
## The same model with decorrelated random effects structure:
sat_no_c <- lmer(
  Saturation_matched ~ Generation + Condition + Generation:Condition + 
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

## Test the necessity of the correlation parameter:
anova(sat_all, sat_no_c, refit = F) 
# correlation not necessary (p = 1)
# We compare sat_all and sat_no_c with refit=F to ensure that no refitting with REML = F happens (default for likelihood ratio tests)

## The same model without random slopes:
sat_no_slopes <- lmer(
  Saturation_matched ~ Generation + Condition + Generation:Condition + 
  (1 | Color_label_matched) +
  (1 | Chain) + 
  (1 | Chain:Subject), 
  data = danish, 
  REML = F, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

## Test the necessity of the random slopes:
anova(sat_no_slopes, sat_no_c, refit = F) 
# slopes are necessary (p < 0.001)
# There is a significant difference, indicating that the slopes do improve the fit
# The model with slopes ("sat_no_c") has a higher log likelihood / lower AIC (= better fit)
# than the model without slopes ("mainm_sat_no_slopes" )
# renaming the model with the best random effects structure
sat_all_main <- sat_no_c
```

Testing fixed effects:
```{r}
## Without interaction:
sat_no_interaction <- lmer(
  Saturation_matched ~ Generation + Condition + 
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

## Generation only
sat_gen_only <- lmer(
  Saturation_matched ~ Generation + 
  (0 + Generation +  Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation +  Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation +  Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

##Condition only
sat_con_only <- lmer(
  Saturation_matched ~ Condition + 
  (0 + Generation +  Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation +  Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation +  Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

##Interaction only
sat_interaction_only <- lmer(
  Saturation_matched ~ Generation:Condition + 
  (0 + Generation +  Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation +  Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation +  Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

##Null model
sat_null <- lmer(
  Saturation_matched ~ 1 +
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

#Testing all fixed effects combination
anova(sat_null, sat_no_interaction, sat_con_only, sat_gen_only, sat_interaction_only, sat_all_main)
```
Notice that when testing for a fixed effect, we keep the random effects structure the same. 

Explanation:
Only two models were significantly different from the null model: 
  "sat_gen_only" - the one where Saturation was predicted by generation as the only fixed effect
      for "sat_gen_only" AIC = 4660.8 and log likelihood = -2294.4
  "sat_interaction_only" - the one where Saturation was predicted by the interaction between generation and condition as the only fixed effect
      for "sat_interaction_only" AIC = 4662.7 and log likelihood = -2294.4

Thus the simplest model which best explains the data is thus the "sat_interaction_only"
```{r}
#Renaming best fit to final saturation model
model1 <- sat_interaction_only
summary(model1)
```
Model outputs:
We see no effect of the interactions in the model which means that our hypothesis has not been confirmed. 
Saturation does not increase over time!

Normality check for model:
```{r}
# We investigate the residuals of the final model:
#histogram
hist(residuals(model1)) # good
#qq-plot
qqnorm(residuals(model1)); qqline(residuals(model1)) # beautiful
#heteroscedasticity
plot(fitted(model1), residuals(model1)) # good
```
Explanation:
Since the residuals look approximately normal (as revealed through histograms and Q-Q plots) there is no problem with the assumption of normality 
As the residual plot looks blob-like, there is no problem with the assumption of homoskedasticity

Investigation of coefficients:
```{r}
#Inspect the random effects estimates
coef(model1) 
```
Explanation:
All subjects, chains and colors have the same intercept that we put to 60% saturation
For chain 1 in condition 2 the slope has a very steep drop of -24
The effect of generation is basically 0 across chains which is also evident from the insignificant fixed effect of generation from the model output


#Modeling Hue
Model comparisons + model runs based on Winter & Wieler 2016 (see method section in thesis for further explanations)
```{r}
## Constructing a mixed model with random slopes for generation, condition and interaction between generation and condition by color, chain, and subjects in chain:
hue_all <- lmer(
  RHAD ~ Generation + Condition + Generation:Condition +
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = F, control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10,
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
```
Explanation:
 - mixed model, modeling relative hue angle difference (RHAD) as a function of generation, condition (presense of color term or not), and the interaction of these with random intercepts (by-chain variation in RHAD, by-color variation in RHAD, and by-subject in chain variation in RHAD) and random slopes for generation, condition and the interaction between generation and condition (by-chain/color/subject variation in the slope of generation, condition and the interaction between generation and condition) and a random intercept / slope correlation. 
 We set REML = T because we want to perform likelihood ratio tests comparing the random effects (for fixed effects it should be REML = F)

Testing random effects:
```{r}
## The same model with decorrelated random effects structure:
hue_no_c <- lmer(
  RHAD ~ Generation + Condition + Generation:Condition + 
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

## Test the necessity of the correlation parameter:
anova(hue_all, hue_no_c, refit = F) 
# correlation is necessary (p < 0.005) so we keep the random structure from "hue"

## The same model without random slopes:
hue_no_slopes <- lmer(
  RHAD ~ Generation + Condition + Generation:Condition + 
  (1 | Color_label_matched) +
  (1 | Chain) + 
  (1 | Chain:Subject), 
  data = danish, 
  REML = F, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

## Test the necessity of the random slopes:
anova(hue_no_slopes, hue_all, refit = F) 
# slopes necessary (p < 0.06)
# There is a (so close to that we accept it) significant difference, indicating that the slopes do improve the fit
hue_all_main <- hue_all
```

Testing fixed effects:
```{r}
##Main effects: Relative hue difference predicted by generation, condition and interaction between the two
## Without interaction:
hue_no_interaction <- lmer(
  RHAD ~ Generation + Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

## Generation only
hue_gen_only <- lmer(
  RHAD ~ Generation + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

##Condition only
hue_con_only <- lmer(
  RHAD ~ Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

##Interaction only
hue_interaction_only <- lmer(
  RHAD ~ Generation:Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

##Null model
hue_null <- lmer(
  RHAD ~ 1 + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))

#Testing all fixed effects combination
anova(hue_null, hue_no_interaction, hue_con_only, hue_gen_only, hue_interaction_only, hue_all_main)
```
Explanation:
Only one model was significantly different from the null model:
    "hue_no_interaction" - the one where Hue difference was predicted by generation and condition as the only fixed effects

Thus the simplest model which best explains the data is the "hue_no_interaction"
```{r}
#Renaming it to final hue model
model2 <- hue_no_interaction

#Final model summary
summary(model2)
```
Explanation:
We see no effect of generation in the model which means that our hypothesis has not been confirmed. 
Hue difference does not decrease over time! But there is a small tendency in directionality indicating that there could be an effect with more studies

Normality checks:
```{r}
## We investigate the residuals of the final model:
#histogram
hist(residuals(model2)) # ok
#QQ-plot
qqnorm(residuals(model2)); qqline(residuals(model2)) # there seem to be some outliers...
#heteroscedasticity
plot(fitted(model2), residuals(model2)) # good
```
Explanation:
Since the residuals look approximately normal (as revealed through histograms and Q-Q plots) there is no problem with the assumption of normality
As the residual plot looks blob-like, there is no problem with the assumption of homoskedasticity

Investigation of coefficients:
```{r}
## Inspect the random effects estimates:

coef(model2) 

```
Interpretation:
Intercepts
For the subjects all intercepts are constant at 96 meaning that they are all close to 100% which would be the seed color - but they are generally tricky to understand
For the chain and color coefficiants the intercepts vary according how far the first generation was from the seed color 

Coefficients within chains
It looks like chain 3 and 4 are the sinners, as they only have positive slopes, where all the others have negative slopes.
Chain 3 seems to have an especially steep positive slope for condition 2
Chain 5 seems to have an especially steep negative slope for condition 2

Coefficients within colors
Dark rose seems to generally produce a positive slope meaning that it converges away from it's focal color but instead towards blue
Grass green seems also to produce positive slopes, and unproportionately much so the condition 2 (+13.5) which would suggest that it converges towards yellow
Mustard seems to generally produce a negative slope meaning that it converges towards it's focal color yellow
Ocean blue also generally seems to produce a negative slope meaning that it converges towards it's focal color blue


#Modeling colors seperately
The interpretations for the coefficients of colors seperately led to this further modelling of colors seperately:
```{r}
model3 <- lmer(
  RHAD ~ Generation:Color_label_matched +
  (1 + Generation + Condition + Generation:Color_label_matched | Chain) +
  (1 + Generation + Condition + Generation:Color_label_matched | Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
      )))
summary(model3)
```
Interpretation:
Fixed effects reveal a different pattern for each seed:
  Dark rose has a significantly positive slope (B=3.7276, p < 0.001), meaning that it converges away from its prototypical hue pair
  Grass green has no effect (B=0.2698, p > 0.05), meaning that it randomly fluctuates
  Mustard has a small negative slope (B=-1.8169, p > 0.05) although insignificant
  Ocean blue has a significantly negative slope (B=-2.5994, p < 0.05), meaning that it converges towards its prototypical hue pair


#Credits
```{r}
#Citations
citation()
citation("lme4")
```












