---
title: "BA analysis test"
author: "Eva SH"
date: "10/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

Setup
```{r setup, include=FALSE}
#Clean environment
rm(list = ls())
#Load
pacman::p_load(readr,dplyr,lme4,lmerTest,mgcv,tidyverse, scales)
```

#Loading and some extra wrangling
```{r}
#setwd("~/Desktop/Cognitive Science/Bachelor/Test data and code/analysis")

###WE NEED TO FIND A SOLUTION WITH RED: IF STATEMENT FOR HUES BETWEEN 0 AND 20? But it works with the current data right now. Think it works. 

data <- read_csv("Cleaned_data/color_matching2020-11-13.csv")


#As factors
data$Subject <- as.factor(data$Subject)
data$Language <- as.factor(data$Language)
data$Gender <- as.factor(data$Gender)
data$Language_spoken <- as.factor(data$Language_spoken)
data$Condition <- as.factor(data$Condition)
data$Chain <- as.factor(data$Chain)
data$Color_label_source <- as.factor(data$Color_label_source)
data$Color_label_matched <- as.factor(data$Color_label_matched)
data$Age <- as.numeric(data$Age)

# #Create column with native language combined: Danish, English, Danish bilingual and other
# data$Language_class <- revalue(data$Language_spoken,c("dansk" = "Danish", "danish" = "Danish","dansker" = "Danish","Dansk" = "Danish","DK"="Danish","Engelsk" = "English", "EnglishandArabic" = "English", "DanskEngelsk" = "Bilingual", "Danskfransk" = "Bilingual", "DanskogBosnisk" = "Bilingual","Danskogengelsk" = "Bilingual", "Danskogsomalisk" = "Bilingual", "NederlandskDansk" = "Bilingual", "Dansksomalisk" = "Bilingual", "Albansk" = "Other", "Croatian" = "Other", "Czech" = "Other", "Estonian" = "Other", "Fransk" = "Other", "geman" = "Other", "German" = "Other", "GermanAfrikaans" = "Other", "Greek" = "Other", "Hollandsk" = "Other", "ita" = "Other", "Lithuanian" = "Other", "Lykke" = "Other", "Polish" = "Other", "polish" = "Other", "portuguese" = "Other", "Romanian" = "Other", "rumænsk" = "Other", "Russian" = "Other", "somalisk" = "Other", "spanish" = "Other", "Spanish" = "Other", "Svensk" = "Other", "Swedish" = "Other", "Ukrainian" = "Other", "Ungarsk" = "Other"))

#Remove chain 5
data <- data %>% filter(!Chain=="5")

#Rescale Confidence
data$Confidence <- rescale(data$Confidence, to = c(1, 7))

#Rename gender for prettier plots
data$Gender <- ifelse(data$Gender == "female", "Female", "Male")

write.csv(data, "data.csv")
```


#Subsets
```{r}
#Datasets divided into Danish and English
danish <- data %>% filter(Language == "Danish")
english <- data %>% filter(Language == "English")

#Subset for each condition
cond1_danish <- danish %>% filter(Condition==1)
cond2_danish <- danish %>% filter(Condition==2)
cond1_english <- english %>% filter(Condition==1)
cond2_english <- english %>% filter(Condition==2)

#Subsets by color
d_red <- danish %>% filter(Color_label_matched == "seed dark rose")
d_yellow <- danish %>% filter(Color_label_matched == "seed mustard")
d_green <- danish %>% filter(Color_label_matched == "seed grass green")
d_blue <- danish %>% filter(Color_label_matched == "seed ocean blue")

#Subsets by color AND condition
d_red_cond1 <- d_red %>% filter(Condition=="1")
d_red_cond2 <- d_red %>% filter(Condition=="2")
d_yellow_cond1 <- d_yellow %>% filter(Condition=="1")
d_yellow_cond2 <- d_yellow %>% filter(Condition=="2")
d_green_cond1 <- d_green %>% filter(Condition=="1")
d_green_cond2 <- d_green %>% filter(Condition=="2")
d_blue_cond1 <- d_blue %>% filter(Condition=="1")
d_blue_cond2 <- d_blue %>% filter(Condition=="2")

```




#Descriptive statistics
```{r}
#Hue maximum, minimum and mean
stats_hue <- danish %>% 
  group_by(Chain, Condition,Color_label_matched) %>% 
  summarise(max(Rel_dif),min(Rel_dif),mean(Hue_matched)) %>% 
  arrange(Color_label_matched)

hue_by_color_overall <- data %>% 
  group_by(Color_label_matched, Condition) %>% 
  summarise(max(Rel_dif), min(Rel_dif), mean(Rel_dif), sd(Rel_dif), max(Rel_dif_2),min(Rel_dif_2), mean(Rel_dif_2), max(Hue_matched), min(Hue_matched), mean(Hue_matched), mean(Seed), mean(Focal), mean(Secondary_focal))


#Saturation
stats_sat <- data %>% 
  group_by(Color_label_matched, Condition) %>% 
  summarise(max(Saturation_matched),min(Saturation_matched),mean(Saturation_matched), sd(Saturation_matched))


```


#Demographics
```{r}
#Load
pacman::p_load(readr,tidyverse,ggplot2,pastecs,ez,reshape2,stringr,lme4,stats,MuMIn,broom,emmeans,afex,lmerTest,scales,rstatix,ggpubr,magrittr,stats)

#Dataframe with 1 row pr subject 
unique <- data[ !duplicated(data$Subject,fromLast=TRUE), ]
unique_danish <- danish[ !duplicated(danish$Subject,fromLast=TRUE), ]
unique_english <- english[ !duplicated(english$Subject,fromLast=TRUE), ]

#In each language
unique %>% count("Language")

#Conditions
unique_danish %>% count("Condition") 
unique_english %>% count("Condition") 

#Gender
#Across conditions
unique_danish %>% count("Gender") 
(100/153) * 85
(100/153) * 68
unique_english %>% count("Gender")
(100/32) * 15
(100/32) * 17

#For each condition
unique_danish %>% filter(Condition=="1") %>% count("Gender") 
(100/78) * 46
(100/78) * 32
unique_danish %>% filter(Condition=="2") %>% count("Gender")
(100/75) * 39 
(100/75) * 36

unique_english %>% filter(Condition=="1") %>% count("Gender") 
(100/16) * 4
(100/16) * 12
unique_english %>% filter(Condition=="2") %>% count("Gender") 
(100/16) * 11
(100/16) * 5

#Age
#Across condition
unique_danish %>% get_summary_stats(Age,type = "mean_sd")
unique_english %>% get_summary_stats(Age,type = "mean_sd")

#For each condition
unique_danish %>% filter(Condition=="1") %>% get_summary_stats(Age,type = "mean_sd")
unique_danish %>% filter(Condition=="2") %>% get_summary_stats(Age,type = "mean_sd")
unique_english %>% filter(Condition=="1") %>% get_summary_stats(Age,type = "mean_sd")
unique_english %>% filter(Condition=="2") %>% get_summary_stats(Age,type = "mean_sd")

#Native languages
#Across conditions
unique_danish %>% count("Language_class")
(100/153) * 136
(100/153) * 1
(100/153) * 7
(100/153) * 9
unique_english %>% count("Language_class")
(100/32) * 22
(100/32) * 5

#For each condition
unique_danish %>%  filter(Condition=="1") %>% count("Language_class")
100/78 * 66
100/78 * 4
100/78 * 8
unique_danish %>%  filter(Condition=="2") %>% count("Language_class")
100/75 * 70
100/75 * 1
100/75 * 3

unique_english %>%  filter(Condition=="1") %>% count("Language_class")
100/16 * 11
100/16 * 2
100/16 * 3
unique_english %>%  filter(Condition=="2") %>% count("Language_class")

```

#Normality checks
```{r}

#Normality (Shapiro-Wilks)
norm_hue <- danish %>% group_by(Chain, Condition, Color_label_matched) %>% shapiro_test(Rel_dif) %>% arrange(Color_label_matched)
ggqqplot(danish, "Rel_dif", ggtheme = theme_bw()) +
  facet_grid(Condition + Color_label_matched ~ Chain, labeller = "label_both")

norm_sat <- danish %>% group_by(Chain, Condition, Color_label_matched) %>% shapiro_test(Saturation_matched)
ggqqplot(danish, "Saturation_matched", ggtheme = theme_bw()) +
  facet_grid(Condition + Color_label_matched ~ Chain, labeller = "label_both")

```


#Modeling Saturation 
```{r}

## Construct mixed model with random slopes for generation, condition and interaction between generation and condition by color, chain, and subjects in chain:
sat <- lmer(
  Saturation_matched ~ Generation + Condition + Generation:Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 + Generation + Condition + Generation:Condition | Chain) + 
  (1 + Generation + Condition + Generation:Condition | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
# Explanation:
# - mixed model modeling level of saturation as a function of generation, condition (sees color name or 
#   not), and the interaction of these
# - with random intercepts (by-chain variation in level of saturation, by-color variation in level of 
#   saturation, and by-subject in chain variation in level of saturation)
# - and random slopes for generation, condition and the interaction between generation and condition 
#   (by-chain/color/subject variation in the slope of generation, condition and the interaction between 
#   generation and condition)
# - and a random intercept / slope correlation
# - we set REML = T because we want to perform likelihood ratio tests 
#   comparing the random effects (for fixed effects it should be REML = F)
#   (The estimates for the variance of the random effects are better
#    when using REML = T.) 
summary(sat)


##Testing random effects##
## The same model with decorrelated random effects structure:
sat_no_c <- lmer(
  Saturation_matched ~ Generation + Condition + Generation:Condition + 
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_no_c)

## Test the necessity of the correlation parameter:
anova(sat, sat_no_c, refit = F) 
# correlation not necessary (p = 1)
# We compare mainm_sat and mainm_sat_no_c with refit=F to ensure that
# no refitting with REML = F happens (default for likelihood ratio tests)

## The same model without random slopes:
sat_no_slopes <- lmer(
  Saturation_matched ~ Generation + Condition + Generation:Condition + 
  (1 | Color_label_matched) +
  (1 | Chain) + 
  (1 | Chain:Subject), 
  data = danish, 
  REML = F, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_no_slopes)

## Test the necessity of the random slopes:
anova(sat_no_slopes, sat_no_c, refit = F) 
# slopes necessary (p < 0.001)
# There is a significant difference, indicating that the slopes do improve the fit
# The model with slopes ("mainm_sat_no_c") has a higher log likelihood / lower AIC (= better fit)
# than the model without slopes ("mainm_sat_no_slopes" )
# renaming the model with the best random effects structure
sat_all_main <- sat_no_c

##Testing fixed effects##

## Without interaction:
sat_no_interaction <- lmer(
  Saturation_matched ~ Generation + Condition + 
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_no_interaction)


## Generation only
sat_gen_only <- lmer(
  Saturation_matched ~ Generation + 
  (0 + Generation +  Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation +  Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation +  Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_gen_only)


##Condition only
sat_con_only <- lmer(
  Saturation_matched ~ Condition + 
  (0 + Generation +  Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation +  Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation +  Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_con_only)

##Interaction only
sat_interaction_only <- lmer(
  Saturation_matched ~ Generation:Condition + 
  (0 + Generation +  Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation +  Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation +  Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_con_only)


##Null model
sat_null <- lmer(
  Saturation_matched ~ 1 +
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_null)

#Testing all fixed effects combination
anova(sat_null, sat_no_interaction, sat_con_only, sat_gen_only, sat_interaction_only, sat_all_main)
# - notice that when testing for a fixed effect, we keep the random effects structure the same
# only two models were significantly different from the null model:
# "sat_gen_only" - the one where Saturation was predicted by generation as the only fixed effect
# "sat_interaction_only" - the one where Saturation was predicted by the interaction between generation and condition as the only fixed effect
# for "sat_gen_only" AIC = 4660.8 and log likelihood = -2294.4
# for "sat_interaction_only" AIC = 4662.7 and log likelihood = -2294.4

#Thus the simplest model which best explains the data is the "sat_interaction_only"
#I will rename it to final saturation model
final_sat <- sat_interaction_only
summary(final_sat)
# We see no effect of the interactions in the model which means that our hypothesis has not been confirmed. 
# Saturation does not increase over time!

## We investigate the residuals of the final model:

hist(residuals(final_sat)) # good
qqnorm(residuals(final_sat)); qqline(residuals(final_sat)) # beautiful
plot(fitted(final_sat), residuals(final_sat)) # good
# Explanation:
# - since the residuals look approximately normal (as revealed through histograms and Q-Q plots)
#   there is no problem with the assumption of normality
# - as the residual plot looks blob-like, there is no problem with the assumption of homoskedasticity??
# check the above!!!

## Inspect the random effects estimates:

coef(final_sat) 
# All subjects, chains and colors have the same intercept that we put to 60% saturation
# for chain 1 in condition 2 the slope has a very steep drop of -24
# the effect of generation is basically 0 across chains which is also evident from the insignificant fixed effect of generation from the model output
```



#Modeling Hue
```{r}
## Construct mixed model with random slopes for generation, condition and interaction between generation and condition by color, chain, and subjects in chain:

hue <- lmer(
  Rel_dif ~ Generation + Condition + Generation:Condition +
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = F, control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10,
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue)

##Testing random effects##

## The same model with decorrelated random effects structure:
hue_no_cor <- lmer(
  Rel_dif ~ Generation + Condition + Generation:Condition + 
  (0 + Generation + Condition + Generation:Condition | Color_label_matched) +
  (1 | Color_label_matched) +
  (0 + Generation + Condition + Generation:Condition | Chain) + 
  (1 | Chain) + 
  (0 + Generation + Condition + Generation:Condition | Chain:Subject) +
  (1 | Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(sat_no_cor)

## Test the necessity of the correlation parameter:
anova(hue, hue_no_cor, refit = F) 
# correlation is necessary (p < 0.005) so we keep the random structure from "hue"

## The same model without random slopes:
hue_no_slopes <- lmer(
  Rel_dif ~ Generation + Condition + Generation:Condition + 
  (1 | Color_label_matched) +
  (1 | Chain) + 
  (1 | Chain:Subject), 
  data = danish, 
  REML = F, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue_no_slopes)

## Test the necessity of the random slopes:
anova(hue_no_slopes, hue, refit = F) 
# slopes necessary (p < 0.06)
# There is a (so close to that we accept it) significant difference, indicating that the slopes do improve the fit
hue_all_main <- hue

##Testing fixed effects##
##Main effects: Relative hue difference predicted by generation, condition and interaction between the two
## Without interaction:
hue_no_interaction <- lmer(
  Rel_dif ~ Generation + Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue_no_interaction)


## Generation only
hue_gen_only <- lmer(
  Rel_dif ~ Generation + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue_gen_only)


##Condition only
hue_con_only <- lmer(
  Rel_dif ~ Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue_con_only)

##Interaction only
hue_interaction_only <- lmer(
  Rel_dif ~ Generation:Condition + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject), 
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue_interaction_only)


##Null model
hue_null <- lmer(
  Rel_dif ~ 1 + 
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject),
  data = danish, 
  REML = T, 
  control = lmerControl(
  optimizer = "nloptwrap",
  calc.derivs = F,
  check.nobs.vs.nRE = "ignore",
  optCtrl = list(
    ftol_abs = 1e-10, 
    xtol_abs = 1e-10,
    maxeval = 10000
  )))
summary(hue_null)

#Testing all fixed effects combination
anova(hue_null, hue_no_interaction, hue_con_only, hue_gen_only, hue_interaction_only, hue_all_main)
# only one model were significantly different from the null model:
# "hue_interaction_only" - the one where Hue difference was predicted by the interaction between generation and condition as the only fixed effect

#Thus the simplest model which best explains the data is the "hue_interaction_only"
#I will rename it to final hue model
final_hue <- hue_interaction_only
summary(final_hue)
# We see no effect of the interactions in the model which means that our hypothesis has not been confirmed. 
# Hue difference does not decrease over time! But there is a small tendency in directionality indicating that there could be an effect with more studies

## We investigate the residuals of the final model:

hist(residuals(final_hue)) # good
hist(log(residuals(final_hue)))
qqnorm(residuals(final_hue)); qqline(residuals(final_hue)) # there seem to be some outliers??
plot(fitted(final_hue), residuals(final_hue)) # good
# Explanation:
# - since the residuals look approximately normal (as revealed through histograms and Q-Q plots)
#   there is no problem with the assumption of normality
# - as the residual plot looks blob-like, there is no problem with the assumption of homoskedasticity

## Inspect the random effects estimates:

coef(final_hue) 
##Intercepts:
# For the subjects all intercepts are constant at 99.6 meaning that they are all close to 100% which would be the seed color - but I generally don't get the slopes
# For the chain and color coefficiants the intercepts vary according how far the first generation was from the seed color 

##Coefficients within chains:
# it looks like chain 3 and 4 are the sinners, as they only have positive slopes, where all the others have negative slopes
# chain 3 seems to have an especially steep positive slope for condition 2
# chain 5 seems to have an especially steep negative slope for condition 2

##Coefficients within colors:
# dark rose seems to generally produce a positive slope meaning that it converges away from it's focal color but instead towards blue
# grass green seems also to produce positive slopes, and unproportionately much so the condition 2 (+13.5) which would suggest that it converges towards yellow
# mustard seems to generally produce a negative slope meaning that it converges towards it's focal color yellow
# ocean blue also generally seems to produce a negative slope meaning that it converges towards it's focal color blue

```


#Modeling colors seperately
```{r}
hue_null <- lmer(
  Rel_dif ~ 1 + Color_label_matched
  (1 + Generation + Condition + Generation:Condition | Color_label_matched) + 
  (1 + Generation + Condition + Generation:Condition| Chain) +
  (1 + Generation + Condition + Generation:Condition| Chain:Subject))

#Effect of color
model3 <- lm(Rel_dif ~ 0 + Color_label_matched * Generation, data = danish)
summary(model3)

model4 <- lm(Saturation_matched ~ 0 + Color_label_matched * Generation, data = danish)
summary(model4)

#Effect of color in interaction with condition
model5 <- lm(Rel_dif ~ 0 + Color_label_matched * Generation * Condition, data = danish)
summary(model5)

model6 <- lm(Saturation_matched ~ 0 + Color_label_matched * Generation * Condition, data = danish)
summary(model6)

#Let's compare the models
# Hue:
anova(model3, model5)
# model 5 is significantly different from model 3, so it would be the best explaining model

# Saturation:
anova(model4, model6)
# again the model with condition is the best fitting model



#Yellow
hue_mustard <- lm(Rel_dif ~ Generation, data = d_yellow)
hue_mustard_with_interaction <- lm(Rel_dif ~ Generation:Condition, data = d_yellow)
hue_mustard_null <- lm(Rel_dif ~ 1, data = d_yellow)
#testing diferent models
anova(hue_mustard_null, hue_mustard, hue_mustard_with_interaction)

summary(hue_mustard)
# the effect of generation has a significantly negative slope of -2.629 (p = 0.0163), meaning that it goes towards yellow as we predicted

#Blue
hue_ocean <- lm(Rel_dif ~ Generation, data = d_blue)
hue_ocean_with_interaction <- lm(Rel_dif ~ Generation:Condition, data = d_blue)
hue_ocean_null <- lm(Rel_dif ~ 1, data = d_blue)
#testing diferent models
anova(hue_ocean_null, hue_ocean, hue_ocean_with_interaction)

summary(hue_ocean_with_interaction)
#the effect of generation has a negative slope for both conditions (cond1: -2.7278, cond2: -0.5031) though only significantly so for condition 1 (p < 0.001) meaning that it goes towards blue as we predicted


#Red
hue_rose <- lm(Rel_dif ~ Generation, data = d_red)
hue_rose_with_interaction <- lm(Rel_dif ~ Generation:Condition, data = d_red)
hue_rose_null <- lm(Rel_dif ~ 1, data = d_red)
#testing diferent models
anova(hue_rose_null, hue_rose, hue_rose_with_interaction)

summary(hue_rose)
# the effect of generation has a significantly positive slope, meaning that it goes towards blue and not red as we predicted

#Green
hue_grass <- lm(Rel_dif ~ Generation, data = d_green)
hue_grass_with_interaction <- lm(Rel_dif ~ Generation:Condition, data = d_green)
hue_grass_null <- lm(Rel_dif ~ 1, data = d_green)
#testing diferent models
anova(hue_grass_null, hue_grass, hue_grass_with_interaction)
# the null model is the best fit, so our predictors doesn't predict anything about the seed color green

```



#Exploratory Analyses 1:
Testing the post hoc hypothesis that for the seed colors that converges in the opporsite direction, they might converge towards their secondary intermediate hues instead of their primary foci

```{r}
#Secondary hues
model7 <- lm(Rel_dif_2 ~ 0 + Color_label_matched * Generation, data = danish)
summary(model7)
# all the slopes for color are significant, but only the red seed, converges towards it's secondary focal (the relative distance becomes smaller: -2.9191 p = < 00.1), namely purple, whereas all other seeds converges away from the secondary focal (the distance becomes bigger)


## Looking at red seperately
hue2_dark_rose <- lm(Rel_dif_2 ~ Generation:Condition, data = d_red)
hue2_dark_rose_no_interaction <- lm(Rel_dif_2 ~ Generation, data = d_red)
hue2_dark_rose_null <- lm(Rel_dif_2 ~ 1, data = d_red)
# testing differences 
anova(hue2_dark_rose_null, hue2_dark_rose, hue2_dark_rose_no_interaction)
# it seems like the interaction model is significantly better than the null model, thus this will be investigated
summary(hue2_dark_rose)
# here their is a significant effect across conditions with a negative slope which means that dark rose is generally converging towards their secondary focal hue, which is purple.
```

#Exploratory Analyses 2:
2: Prdicting accuracy
```{r}
pacman::p_load(ggpubr, NCmisc, RColorBrewer, unikn)
#Increased levels of confidence predicts accuracy
# Descriptive
stats_acc <- data %>% 
  group_by(Gender, Color_label_matched) %>% 
  summarise(min(Accuracy_hue),max(Accuracy_hue),mean(Accuracy_hue),sd(Accuracy_hue),min(Accuracy_sat),max(Accuracy_sat),mean(Accuracy_sat),sd(Accuracy_sat),mean(Confidence),sd(Confidence)) %>% 
  arrange(Color_label_matched)

## Outliers
# outliers1 <- which.outlier(data$Accuracy_hue)
# outliers2 <- which.outlier(data$Accuracy_sat)
outliers_hue <- boxplot(data$Accuracy_hue, plot=FALSE)$out
outliers_sat <- boxplot(data$Accuracy_sat, plot=FALSE)$out
#remove outliers
data_no_outliers_hue<- data[-which(data$Accuracy_hue %in% outliers_hue),]
data_no_outliers_sat<- data[-which(data$Accuracy_sat %in% outliers_sat),]

## Simple models
#Hypothesis: accuracy will decrease if confidence goes up
#For hue
hue_acc_con <- lm(Accuracy_hue ~ Confidence:Gender, data = data_no_outliers_hue)
summary(hue_acc_con)
#For saturation
sat_acc_con <- lm(Accuracy_sat ~ Confidence:Gender, data = data_no_outliers_sat)
summary(sat_acc_con)



```

By color for hue
```{r}
##By color for hue

#red
acc_hue_r <- ggplot(d_red, aes(x = Confidence, y = Accuracy_hue))+
  geom_smooth(color="#cc3386",fill="#cc3386", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#cc3386"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching hue",
       subtitle = "Seed dark rose",
       title = "\n")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_hue_r
#green
acc_hue_g <- ggplot(d_green, aes(x = Confidence, y = Accuracy_hue))+
  geom_smooth(color="#38cc33",fill="#38cc33", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#38cc33"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching hue",
       subtitle = "Seed grass green")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_hue_g
#blue #33ccca"
acc_hue_b <- ggplot(d_blue, aes(x = Confidence, y = Accuracy_hue))+
  geom_smooth(color="#33ccca",fill="#33ccca", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#33ccca"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching hue",
       subtitle = "Seed ocean blue",
       title = "\n")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title =element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_hue_b

#yellow "#ccb233"
acc_hue_y <- ggplot(d_yellow, aes(x = Confidence, y = Accuracy_hue))+
  geom_smooth(color="#ccb233",fill="#ccb233", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#ccb233"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching hue",
       subtitle = "Seed mustard")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_hue_y

#placing them next to each other
accuracy_hue <- ggarrange(acc_hue_r, acc_hue_b, acc_hue_g, acc_hue_y, labels = "Accuracy predicted by confidence - with outliers", hjust = -0.1, font.label = list(size = 12))
# Save the plot to a pdf
ggsave("accuracy_hue.png")

#Same plot without outliers
range(data_no_outliers_hue$Accuracy_hue)
acc_hue_r2<-acc_hue_r %+% d_red[d_red$Accuracy_hue<14,]
acc_hue_g2<-acc_hue_g %+% d_green[d_green$Accuracy_hue<14,]
acc_hue_b2<-acc_hue_b %+% d_blue[d_blue$Accuracy_hue<14,]
acc_hue_y2<-acc_hue_y %+% d_yellow[d_yellow$Accuracy_hue<14,]
accuracy_hue_no_outs <- ggarrange(acc_hue_r2, acc_hue_b2, acc_hue_g2, acc_hue_y2, labels = "Accuracy predicted by confidence - without outliers", hjust = -0.1, font.label = list(size = 12))

# Save the plot to a pdf
ggsave("accuracy_hue_no_outs.png")
```

By color for saturation
```{r}
##By color for saturation
#red
acc_sat_r <- ggplot(d_red, aes(x = Confidence, y = Accuracy_sat))+
  geom_smooth(color="#cc3386",fill="#cc3386", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#cc3386"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching saturation",
       subtitle = "Seed dark rose",
       title = "\n")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_sat_r
#green
acc_sat_g <- ggplot(d_green, aes(x = Confidence, y = Accuracy_sat))+
  geom_smooth(color="#38cc33",fill="#38cc33", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#38cc33"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching saturation",
       subtitle = "Seed grass green")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_sat_g
#blue #33ccca"
acc_sat_b <- ggplot(d_blue, aes(x = Confidence, y = Accuracy_sat))+
  geom_smooth(color="#33ccca",fill="#33ccca", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#33ccca"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching saturation",
       subtitle = "Seed ocean blue",
       title = "\n")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_sat_b

#yellow "#ccb233"
acc_sat_y <- ggplot(d_yellow, aes(x = Confidence, y = Accuracy_sat))+
  geom_smooth(color="#ccb233",fill="#ccb233", method="lm") +
  geom_point(aes(color=Gender))+
  scale_color_manual(values = c(brew_mix[3], brew_mix[11], "#ccb233"))+
  labs(x = "Confidence", 
       y ="Accuracy of matching saturation",
       subtitle = "Seed mustard")+
  scale_x_continuous(breaks = 1:7)+
  theme_minimal() + theme(
    axis.title=element_text(size=9),
    legend.position = "none")+
  facet_wrap(~ Gender)
acc_sat_y

#placing them next to each other
accuracy_sat <- ggarrange(acc_sat_r, acc_sat_b, acc_sat_g, acc_sat_y, labels = "Accuracy predicted by confidence - with outliers", hjust = -0.1, font.label = list(size = 12))
# Save the plot to a pdf
ggsave("accuracy_sat.png")

range(data_no_outliers_sat$Accuracy_sat)
acc_sat_r2<-acc_sat_r %+% d_red[d_red$Accuracy_sat<24,]
acc_sat_g2<-acc_sat_g %+% d_green[d_green$Accuracy_sat<24,]
acc_sat_b2<-acc_sat_b %+% d_blue[d_blue$Accuracy_sat<24,]
acc_sat_y2<-acc_sat_y %+% d_yellow[d_yellow$Accuracy_sat<24,]
accuracy_sat_no_outs <- ggarrange(acc_sat_r2, acc_sat_b2, acc_sat_g2, acc_sat_y2, labels = "Accuracy predicted by confidence - without outliers", hjust = -0.1, font.label = list(size = 12))

# Save the plot to a pdf
ggsave("accuracy_sat_no_outs.png")

```



```{r}
plot <- ggplot(d_red, aes(x = Generation, y = Rel_dif_2, group = Chain, color = Chain))+
  geom_line(stat="summary") +
  expand_limits(y=0) +
  xlab("Generation") + 
  ylab("RD %") +
  ggtitle("Plot saturation green") +
  facet_wrap(~ Condition)+
  scale_color_viridis_d(begin=0.3,end=0.9,option = "D") + 
  theme_light()
plot
```

#Credits
```{r}
#Citations
citation()
citation("lme4")
```












